AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-10 publications/iaai21/dora_outlier_detection_iaai.tex
add dora configurable pipeline and negative sampling paragraphs #42

\subsection{DORA configurable pipeline} 
Figure \ref{fig:dora} illustrates the architecture of DORA.
\todo{Steven please add a couple sentences about the
approach/design choices for this pipeline.} \todo{Describe the configuration
file setup. Discuss definitions of data to fit and data to score.
Maybe include example files in the appendix?}
We designed DORA to be readily extensible to support additional data types or 
formats, outlier detection algorithms, and results organization or 
visualization methods by writing new modules that follow the DORA API.

@@

\subparagraph{Likelihood.}
\todo{Describe PAE: Hannah or Bryce (if it is ready to be included.)}
\todo{Describe negative sampling: Steven.}

>>>>

\subsection{DORA configurable pipeline} 
Figure \ref{fig:dora} illustrates the architecture of DORA. It includes 
data loading, feature extraction, outlier ranking, results organization, and 
results visualizaiton modules. The DORA pipeline is implemented in Python 3.
In order to improve the readability and execution speed of the code, we adopted
object-oriented and functional programming practices.  We designed DORA to be 
readily extensible to support additional data types or formats, outlier detection 
algorithms, and results organization or visualization methods by writing new 
modules that follow the DORA API. Experimental settings are controlled by 
configuration files. In a configuration file, users can specify the input data, 
feature extraction methods, normalization method, outlier ranking methods, and 
results organization methods.

@@

\subparagraph{Likelihood.}
\todo{Describe PAE: Hannah or Bryce (if it is ready to be included.)}
The negative sampling algorithm is implemented by converting the unsupervised 
outlier ranking problem into a semi-supervised problem. Negative (anomalous) 
examples are created by sampling from a expanded space defined by the minimum 
and maximum values of each dimension of the positive (normal) examples. The 
negative and positive examples are then used to train a random forest 
classifier. We use the posterior probabilities of the random forest classifier 
as outlier scores, which means that the observations with higher posterior 
probabilities are more likely to be outliers.
